A Horrocks-type theorem for even orthogonal $K_2$

### 2020-04-08 dl-paper.tex
Fix bug

We need one more technical definition. Denote by $Z_{\alpha, \beta}$ the subgroup $U(Z_+(\alpha) \setminus \{\alpha - \beta \}, M[X])$ of $\St(\Phi, A[X, X^{-1}])$.  Recall that this means that $Z_{\alpha, \beta}$ is generated by all root subgroups $X_\gamma(M[X])$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$. It is clear that $Z_{\alpha,\beta} \subseteq j_+(Z_\alpha(A, M))$.

@@

It remains to verify the assertion for the generators $x_{-\alpha}(X^2f) $ of type K2.
By~\cref{K-a-b-cor} we may assume that the root $\delta$ in~\cref{def:Kab} forms a sharp angle with $\alpha$, i.\,e. $\alpha-\delta \in \Phi$. Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = \delta-\alpha$ into~\eqref{Z5} we obtain that
\begin{multline*} z_{-\alpha}(X^2f, aX^{-1}) = x_{\delta-\alpha}(\epsilon Xf) \cdot x_{\delta}(-af) \cdot x_{-\delta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
 \cdot z_{\delta-\alpha}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha-\delta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{\delta}(a f, -X), \end{multline*}
where $\epsilon = N_{-\delta,\alpha}$. 
The first 7 factors in the right-hand side are generators of type K1, Z, K1, K2, K1, K1, Z.
The remaining last factor $z_\delta(af, -X)$ can be rewritten as $x_{\delta}(af) \cdot c_{\delta}(-af, X)$ (cf.~\cref{rem:c}), which is a product of generators of type Z and K5. \end{proof}

@@

It is clear that the specified conjugation centralizes $j_+(Z_\alpha(A, M))$ (and hence $Z_{\alpha, \beta}$). By~\eqref{Chevalley-CCF1} and~\cref{rem:recognition} 
$X_{-\beta}(M\cdot X)^{x_\alpha(aX^{-1})} \subseteq X_{-\beta}(M\cdot X) \cdot X_{\alpha-\beta}(M) \subseteq P_\alpha(0).$ Finally, from~\cref{image-K-a-b} we get that
$K(\alpha, \beta)^{x_\alpha(aX^{-1})} \subseteq \langle K(\alpha, \beta), Z_{\alpha, \beta} \rangle \subseteq P_\alpha(0)$.
\end{proof}

>>>>

We need one more technical definition. Denote by $Z_{\alpha, \beta}$ the subgroup $U(Z_+(\alpha) \setminus \{\alpha - \beta \}, M[X])$ of $\St(\Phi, A[X, X^{-1}])$.  Recall that this means that $Z_{\alpha, \beta}$ is generated by all root subgroups $X_\gamma(M[X])$, where $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.

@@

It remains to verify the assertion for the generators $x_{-\alpha}(X^2f) $ of type K2.
By~\cref{K-a-b-cor} we may assume that the root $\delta$ in~\cref{def:Kab} forms a sharp angle with $\alpha$, i.\,e. $\alpha-\delta \in \Phi$. Substituting $s = Xf$, $\eta = X$, $\xi = aX^{-1}$ and $\alpha = \delta-\alpha$ into~\eqref{Z5} we obtain that
\begin{multline*} z_{-\alpha}(X^2f, aX^{-1}) = x_{\delta-\alpha}(\epsilon Xf) \cdot x_{\delta}(-af) \cdot x_{-\delta}(aX^2 f) \cdot x_{-\alpha}(X^2f) \cdot \\
 \cdot z_{\delta-\alpha}(-\epsilon Xf, -\epsilon a) \cdot x_{\alpha-\delta}(-\epsilon a^2 Xf) \cdot x_{\alpha}(- a^2 f) \cdot z_{\delta}(a f, -X), \end{multline*}
where $\epsilon = N_{-\delta,\alpha}$. 
The first 7 factors in the right-hand side are generators of type K1, Z, K1, K2, K1, K1, Z.
The remaining last factor $z_\delta(af, -X)$ can be rewritten as $x_{\delta}(af) \cdot c_{\delta}(-af, X)$ (cf.~\cref{rem:c}) and hence is a product of generators of type Z and K5. \end{proof}

@@

It is clear that the specified conjugation centralizes $j_+(Z_\alpha(A, M))$. By~\eqref{Chevalley-CCF1} and~\cref{rem:recognition} 
$X_{-\beta}(M\cdot X)^{x_\alpha(aX^{-1})} \subseteq X_{-\beta}(M\cdot X) \cdot X_{\alpha-\beta}(M) \subseteq P_\alpha(0).$ 
Notice that the generators of $Z_{\alpha,\beta}$ are generators of type P2 for $P_\alpha(0)$.
Thus, from~\cref{image-K-a-b} we get that
$K(\alpha, \beta)^{x_\alpha(aX^{-1})} \subseteq \langle K(\alpha, \beta), Z_{\alpha, \beta} \rangle \subseteq P_\alpha(0)$.
\end{proof}
